% (c)	Publications
%
% A list of: (i) up to 5 publications most closely related to the
% proposed project; and (ii) up to 5 other significant publications,
% whether or not related to the proposed project. Each publication
% identified must include the names of all authors (in the same sequence
% in which they appear in the publication), the article and journal
% title, book title, volume number, page numbers, and year of
% publication. If the document is available electronically, the website
% address also should be identified.
%
% For unpublished manuscripts, list only those submitted or accepted for
% publication (along with most likely date of publication). Patents,
% copyrights and software systems developed may be substituted for
% publications. Additional lists of publications, invited lectures,
% etc., must not be included. Only the list of 10 will be used in the
% review of the proposal.

\subsection*{Selected Publications}

\begin{enumerate}

\item{Schneider, M. D., \ldots, \textbf{Marshall, P. J.} et al\\
\textit{Hierarchical probabilistic inference of cosmic shear}\\
ApJ accepted, 2015.
\texttt{http://arxiv.org/abs/1411.2608}
}

\item{{Brewer}, B.~ J., \textbf{Marshall, P.~J.} et al\\
\textit{The SWELLS survey - VI. Hierarchical inference of the initial mass functions of bulges and discs}\\
MNRAS, \textbf{437}, 1950, 2014.
\texttt{http://arxiv.org/abs/1310.5177}
}

\item{{Suyu}, S.~H., \ldots, \textbf{{Marshall}, P.~J.} et al\\
\textit{Cosmology from gravitational lens time delays and Planck data}\\
ApJ, \textbf{788}, 35, 2014.
\texttt{http://arxiv.org/abs/1306.4732}
}

\item{Collett, T.~E., \textbf{Marshall, P.~J.}, et al\\
\textit{Reconstructing the lensing mass in the Universe from photometric catalogue data}\\
MNRAS, \textbf{432}, 679, 2013.
\texttt{http://arxiv.org/abs/1303.6564}
}

\item{{Ivezic}, Z., \ldots, \textbf{{Marshall}, P.~J.}, and the LSST Collaboration.\\
\textit{LSST: from Science Drivers to Reference Design and Anticipated Data Products}\\
\texttt{http://arxiv.org/abs/0805.2366},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item{\textbf{Marshall, P. J.} et al\\
\textit{Space Warps -- I. Crowd-sourcing the Discovery of Gravitational Lenses}\\
MNRAS accepted, 2015.
\texttt{http://arxiv.org/abs/1504.06148}
}

\item{Sonnenfeld, Alessandro, \ldots, \textbf{Marshall, P.~J.} et al\\
\textit{The SL2S Galaxy-scale Lens Sample. V. Dark Matter Halos and Stellar IMF of Massive ETGs out to Redshift 0.8}\\
ApJ, \textbf{800}, 94, 2015.
\texttt{http://arxiv.org/abs/1410.1881}
}

\item{{Busha}, M.~T., \textbf{{Marshall}, P.~J.}, et al\\
\textit{The Mass Distribution and Assembly of the Milky Way from
the Properties of the Magellanic Clouds}\\
ApJ, \textbf{743}, 40, 2011.
\texttt{http://arxiv.org/abs/1011.2203}
}

\item{Oguri, M., \& \textbf{Marshall, P.J.}\\
\textit{Gravitationally lensed quasars and supernovae in future wide-field
optical imaging surveys}\\
MNRAS, \textbf{405}, 2579, 2010.
\texttt{http://arxiv.org/abs/1001.2037}
}

\item{Suyu, S., \textbf{{Marshall}, P.~J.}, Hobson, M.~P. \& Blandford, R.~D.\\
\textit{A Bayesian analysis of regularised source inversions in gravitational lensing}\\
MNRAS, \textbf{371}, 983, 2006.
\texttt{http://arxiv.org/abs/0601493}
}

\end{enumerate}



% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
