% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection*{Contributions to Symposia (invited)}

\begin{itemize}

\item{\textbf{Marshall, P.~J.}:
\textit{LSST Observing Strategy: the Time Delay Challenge, and Cadence Diplomacy},
special session invited talk at the {American Astronomical Society Meeting}, 2016.
}

\item{\textbf{Marshall, P.~J.}:
\textit{Weighing Halos by Sampling Cosmological Simulations},
invited talk at ``Innovative Cosmological Simulations with Machine Learning and Statistics in the era of LSST,'' Carnegie Mellon University, 2015.
}

\item{\textbf{Marshall, P.~J.} et al:
\textit{Feeding the Giants with LSST},
invited review at the {ESO Workshop ``Feeding the Giants: ELTs in the Era of Surveys}, Ischia, 2011.''
}

\item{\textbf{Marshall, P.~J.}:
\textit{Extragalactic Science with LSST},
special session review at the {American Astronomical Society Meeting}, 2011.
}

\end{itemize}

\vspace{2\baselineskip}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection*{Contributions to Symposia (refereed)}

\begin{itemize}

\item{McKean, J., \ldots, \textbf{Marshall, P.J.} et al:
\textit{Strong Gravitational Lensing with the SKA}
Proceedings of ``Advancing Astrophysics with the Square Kilometre Array'' (AASKA14), 2014.
\texttt{astro-ph/1502.03362}
}

\item{{Moustakas}, L.~A., \dots, \textbf{Marshall, P.~J.}, et al:
\textit{The Observatory for Multi-Epoch Gravitational Lens Astrophysics (OMEGA)},
Proceedings of the SPIE (Astronomical Telescopes and Instrumentation), 2008.
\texttt{astro-ph/0806.1884}
}

\item{\textbf{Marshall, P.~J.}, Roger Blandford \& Masao Sako:
\textit{The SNAP Strong Lens Survey},\\
in ``Wide Field Imaging from Space'' (New Astronomy Reviews), Elsevier Science, 2004.
\texttt{astro-ph/0501328}
}

\item{{Blandford}, R.~D., \ldots, \textbf{{Marshall}, P.~J.} et al:
\textit{Cosmokinetics},
in ``Observing Dark Energy'' (Proceedings of the NOAO Workshop, Tucson), ASP conference series, 2004.
\texttt{astro-ph/0408279}
}

\item{\textbf{{Marshall}, P.~J.,} {Hudelot}, P. \& {Kneib}, J.-P:
\textit{Multiple Component Analysis of Cluster Lenses},
in ``Exploring the Universe'' (Proceedings of the XXXIXth Rencontres de Moriond), EDP Sciences, 2004.
}

\item{\textbf{Marshall, P.J.} et al:
\textit{Cosmology from Cluster SZ and Weak Lensing Data},
in ``The Cosmological Model'' (Proceedings of the XXXVIIth Rencontres de Moriond), EDP Sciences, 2002.
\texttt{astro-ph/0205345}
}

\end{itemize}

\vspace{2\baselineskip}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection*{Contributions to Symposia (unrefereed)}

\begin{itemize}

\item{Schneider, M., \ldots, \textbf{Marshall, P.~J.} et al\\
\textit{Inferring the Intrinsic Ellipticity Distribution of Galaxies}\\
presented at the {American Astronomical Society Meeting}, 2015.
}

\item{Rumbaugh, N., \ldots, \textbf{Marshall, P.~J.} et al\\
\textit{Radio and Gamma-Ray Monitoring of Strongly Lensed Quasars and Blazars}\\
presented at the {American Astronomical Society Meeting}, 2015.
}

\item{Sonnenfeld, A., \ldots, \textbf{Marshall, P.~J.} et al\\
\textit{The evolution of early-type galaxies: a strong lensing perspective}\\
presented at the {American Astronomical Society Meeting}, 2015.
}

\item{Sandford, E., \ldots, \textbf{Marshall, P.~J.} et al\\
\textit{Machine Learning Identification of Dwarf Galaxy Satellites around Milky Way Analogs}\\
presented at the {American Astronomical Society Meeting}, 2014.
}

\item{Liao, K., \ldots, \textbf{Marshall, P.~J.} et al\\
\textit{The Strong Lensing Time Delay Challenge (2014)}\\
presented at the {American Astronomical Society Meeting}, 2014.
}

\item{\textbf{Marshall, P.~J.} and the LSST Dark Energy Science Collaboration:
\textit{How to Measure Dark Energy with LSST's Strong Gravitational Lenses}\\
presented at the {American Astronomical Society Meeting}, 2013.
}

\item{{Moustakas}, L., \ldots \textbf{Marshall, P.~J.} and the OMEGA Explorer Science Team:
\textit{Strong Gravitational Lensing Insights into Dark Matter Physics}\\
presented at the {American Astronomical Society Meeting}, 2013.
}

\item{\textbf{Marshall, P.~J.} et al:
\textit{Accurate Cosmography with LSST Time Delay Lenses},
presented at the {RAS National Astronomy Meeting}, 2011.
}

\item{\textbf{Marshall, P.~J.} et al:
\textit{Accurate Cosmography with LSST Time Delay Lenses},
presented at the {American Astronomical Society Meeting}, 2011.
}

\item{Jernigan, J.~G., \textbf{Marshall, P.~J.} et al:
\textit{Strong Lenses with LSST: Simulated 10-year Movies of Multiply-Imaged
Quasars}, presented at the {American Astronomical Society Meeting}, 2011.
}

\item{Nierenberg, A., \ldots, \textbf{Marshall, P.~J.} et al:
\textit{Luminous Satellites of Early-Type Galaxies I: Spatial Distribution},
presented at the {American Astronomical Society Meeting}, 2011.
}

\item{\textbf{Marshall, P.~J.}:
\textit{Strong Gravitational Lensing with LSST},
presented at the {American Astronomical Society Meeting}, 2010.
}

\item{Naudus, P., Wallin, J., \& \textbf{Marshall, P.~J.}:
\textit{Computer Modeling of Gravitational Lensing Systems},
presented at the {American Astronomical Society Meeting}, 2010.
}

\item{\textbf{Marshall, P.~J.}:
\textit{The HST Archive Galaxy-scale Gravitational Lens Search},
presented at the {American Astronomical Society Meeting}, 2009.
}

\item{{Lagattuta}, D.~J., \dots, \textbf{Marshall, P.~J.}, et al:
\textit{A Weak Lensing Analysis of Moderate Redshift Strong Lenses},
presented at the {American Astronomical Society Meeting}, 2009.
}

\item{{Keeton}, C.~R., \ldots, \textbf{Marshall, P.~J.}, et al:
\textit{LSST Strong Lensing: Galaxies And Their Nuclei Under A Gravitational Microscope},
presented at the {American Astronomical Society Meeting}, 2009.
}

\item{\textbf{Marshall, P.~J.}:
\textit{Robotic Searches for Strong Gravitational Lenses},
presented at OZ Lens 2008:
``Dark Matter, Dark Energy and Dark Ages with Gravitational Lensing'', Sydney
2008.
}

\item{\textbf{Marshall, P.~J.} \& Treu, T.:
\textit{Exotic Lenses},
presented at the CITA workshop
``Upcoming Lensing surveys: Beyond The Obvious,'' Toronto 2008.
}

\item{\textbf{Marshall, P.~J.}:
\textit{First results from HAGGLeS},
presented at the XXIIIrd IAP Colloquium
``From giant arcs to CMB lensing: 20 years of gravitational distortion,'' 2007.
}

\item{\textbf{Marshall, P.~J.}, et al:
\textit{Future Surveys: SNAP and LSST},
presented at the Fermilab conference
``Searching for Strong Lenses in Large Imaging Surveys,'' 2007.
}

\item{{Blandford}, R.~D., \dots, \textbf{Marshall, P.~J.}, and the {LSST collaboration}:
\textit{Gravitationally Lensed Quasars: Lessons from SDSS and Predictions for LSST},
presented at the {American Astronomical Society Meeting}, 2007.
}

\item{{Brada\v{c}}, M., \ldots, \textbf{Marshall, P.~J.}, et al:
\textit{Dark Matter in Galaxy Cluster 1E0657-56: Measuring the Invisible With Gravitational Lensing},
presented at the {American Astronomical Society Meeting}, 2007.
}

\item{{Moustakas}, L.~A., \textbf{Marshall, P.} and {AEGIS Collaboration}:
\textit{A Three-Dimensional View of the Environments of Three Strong Gravitational Lenses},
presented at the {American Astronomical Society Meeting}, 2007.
}

\item{{Suyu}, S.~H., \ldots, \textbf{Marshall, P.~J.} et al:
\textit{HST ACS Observations of the Gravitational Lens B1608+656},
presented at the {American Astronomical Society Meeting}, 2007.
}

\item{\textbf{Marshall, P.~J.}:
\textit{Future Searches for Lenses},
presented at the KITP Conference: Applications of Gravitational Lensing:
Unique Insights into Galaxy Formation and Evolution, 2006.
}

\item{\textbf{{Marshall}, P.~J.} et al:
\textit{Automated searching for lenses in high resolution images},
presented at the {Oort Workshop on Gravitational Lensing}, Leiden 2006.
}

\item{\textbf{{Marshall}, P.~J.} et al:
\textit{An Automated Search for Gravitational Lenses in the HST Imaging Archive},
presented at the {American Astronomical Society Meeting}, 2006.
}

\item{{Baltz}, E.~A., {Blandford}, R.~D. and \textbf{Marshall, P.~J.}:
\textit{Higher-order Catastrophes in Gravitational Lenses},
presented at the {American Astronomical Society Meeting}, 2006.
}

\item{{Kirkby}, L., \textbf{Marshall, P.~J.} and the {LSST Collaboration}:
\textit{Measuring Strong Gravitational Lens Time Delays with the LSST},
presented at the {American Astronomical Society Meeting}, 2006.
}

\item{{Fassnacht}, C.~D., \textbf{{Marshall}, P.~J.} et al:
\textit{Strong Lensing Studies with the LSST},
presented at the {American Astronomical Society Meeting}, 2005.
}

\item{{Peterson}, J.~R., \textbf{{Marshall}, P.~J.} \& {Andersson}, K:
\textit{A Non-Parametric Approach to Modeling Clusters of Galaxies},
presented at {AAS/High Energy Astrophysics Division} meeting, 2004.
}

\item{\textbf{Marshall, P.J}:
\textit{Evidence for Structure in Weak Lensing Maps},
in ``A New Era in Cosmology'' (Proceedings of the Durham conference), ASP conference series, 2001.
}

\item{\textbf{Marshall, P.J}:
\textit{Maximum-Entropy Reconstruction of the Distribution of Mass in Cluster MS1054-03 from Weak Lensing Data},
in ``Galaxy Clusters and the High-Redshift Universe Observed in X-rays,''
(Proceedings of the XXIst Moriond Astrophyics Meeting), EDP Sciences, 2001.
\texttt{astro-ph/0106025}
}
\end{itemize}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
